---
title: "Exam Performance"
author: "A.S., D.O."
date: "December 5, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

http://roycekimmons.com/tools/generated_data/exams
This dataset found on kaggle was pulled from this website. It is theoretically "exam scores for students at a public school". However, there is an interesting disclaimer at the end that says "All data sets are fictional and should be used for educational purposes only." That is a :thinking:

## Package Load

```{r}
library(dplyr)
library(ggplot2)
```

## Load Data

```{r}
full <- read.csv("StudentsPerformance.csv", header = TRUE)
dim(full)
head(full)
str(full)
```

So it doesn't seem like this dataset is too big. It's a smaller sample, relatively speaking. 1000 isn't a copious amount.

We've got 5 indicators about people, their gender, their race (as described in a group, we don't know which correlate to which), their parents' level of education, their lunch situation (probably pointing to their financial situation), and whether they did a test prep course.

To analyze, we have their writing, reading, and math scores.

## Select Data
```{r}
math_score <- full$math.score
ave_math <- mean(math_score)
reading_score <- full$reading.score
ave_reading <- mean(reading_score)
writing_score <- full$writing.score
ave_writing <- mean(writing_score)

ave_math
ave_reading
ave_writing

```